\tnoteref{note1}Training Feedforward Neural Networks with Bayesian Hyper-Heuristics

### 2024-01-11 article/main.tex
💚 Dedicated to Taylah, Beané and Aleah

\usepackage{acro}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{url}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{multirow}

@@

	\affiliation[aff:tuks]{
		organization={University of Pretoria},
		% addressline={Lynnwood Rd},
		city={Pretoria},
		postcode={0002},
		state={Gauteng},
		country={South Africa}
	}

	\affiliation[aff:stellenbosch]{
		organization={Stellenbosch University},
		% addressline={Ryneveld Street},
		city={Stellenbosch},
		postcode={7602},
		state={Western Cape},
		country={South Africa}
	}

	\affiliation[aff:wits]{
		organization={University of the Witwatersrand},
		% addressline={1 Jan Smuts Ave},
		city={Johannesburg},
		postcode={2000},
		state={Gauteng},
		country={South Africa}
	}

	\author[aff:tuks]{\corref{cor1}A.N.~Schreuder}
	\ead{an.schreuder@up.ac.za}
	\author[aff:tuks]{A.S.~Bosman}
	\ead{annar@cs.up.ac.za}
	\author[aff:stellenbosch]{A.P.~Engelbrecht}
	\ead{engel@sun.ac.za}
	\author[aff:wits]{C.W.~Cleghorn}
	\ead{christopher.cleghorn@wits.ac.za}

@@

@@

A popular field of focus for studying \acfp{ANN} is the process by which these models are trained. \acp{ANN} are trained by optimisation algorithms known as heuristics. Many different heuristics have been developed and used to train \acp{ANN} \citep{ref:rakitianskaia:2012}. Each of these heuristics has different search behaviours, characteristics, strengths and weaknesses. It is necessary to find the best heuristic to train \acp{ANN} in order to yield optimal results. This process is often non-trivial and time-consuming. Selection of the best heuristic to train \acp{ANN} is often problem specific \citep{ref:allen:1996}.

@@

This research takes a particular interest in developing a population-based, selection \acs{HH} that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process. This paper presents a novel \acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution. This selection probability distribution is the mechanism by which the \acs{HH} selects appropriate heuristics to train \acp{FFNN} during the training process.

@@

@@

% ARTIFICIAL NEURAL NETWORKS
\section{Artifical Neural Networks}
\label{sec:anns}

@@

The biggest difference between \acp{MH} and gradient-based heuristics is that \acp{MH} make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search space \citep{ref:blum:2003}. This also means that \acp{MH} do not necessarily require the error function to be differentiable. \citet{ref:blum:2003} provides advantages of \acp{MH} that include the following: they are easy to implement, they are problem independent and do not require problem-specific knowledge, and they are generally designed to find global optima, while gradient-based approaches can get stuck in local optima more often. Similar to gradient-based heuristics, a number of different meta-heuristics have been used to successfully train \acp{FFNN} \citep{ref:rakitianskaia:2012, ref:vanwyk:2014, ref:gupta:1999}. This research takes a particular interest in population-based \acp{MH} that have been used to train \acp{FFNN}. These include \acf{PSO} \citep{ref:shi:1998}, \acf{DE} \citep{ref:price:2006} and \acfp{GA} \citep{ref:fraser:1957}.

@@

\citet{ref:burke:2010} proposed a classification scheme used to classify \acp{HH}. According to the proposed classification scheme, \acp{HH} are classified in two dimensions. These include the \textit{source of feedback} used during learning and the nature of the \textit{heuristic search space}. For the dimension that involves the source of feedback, \acp{HH} can be classified as either \textit{no learning}, \textit{online learning} or \textit{offline learning}. For the dimension that involves the nature of the \textit{heuristic search space}, \acp{HH} can be classified as either \textit{heuristic selection} or \textit{heuristic generation}. Further distinction is made between \textit{construction} of heuristics and \textit{perturbation} of heuristics.

@@

In general, there are two main views to probability and statistics. These include the \textit{frequentist} and the \textit{Bayesian} view of statistics. Naturally, Bayesian statistics is based on Bayes' theorem \citep{ref:bayes:1763}.

@@

This section presents the novel \acs{BHH}. The general concept of the \acs{BHH} is summarised as follows: the \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics. These low-level heuristics are applied to a population of entities, each implementing a candidate solution to a \acs{FFNN}. The  intent of the \acs{BHH} is to optimise both the underlying \acs{FFNN} and the \acs{FFNN} training process. The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process. These probabilities are then used as heuristic selection probabilities in the next step of the training process.

According to the classification scheme for \acp{HH} by \citet{ref:burke:2010}, the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion. Figure \ref{fig:bhh_architecture} provides an illustration of the high-level architecture of the \acs{BHH}. Algorithm \ref{algo:bhh} provides the high level pseudo-code implementation of the \acs{BHH}. Discussions follow on the most important components of the \acs{BHH}.

@@

\begin{equation}
	\label{eq:bhh:optimisation_step:map:alpha_update_operation}
	\begin{split}
		\alpha_{k}(t+1) = N_{k} + \alpha_{k}(t)
	\end{split}
\end{equation}

\begin{equation}
	\label{eq:bhh:optimisation_step:map:beta_update_operation}
	\begin{split}
		\beta_{j,k}(t+1) = N_{j,k} + \beta_{j,k}(t)
	\end{split}
\end{equation}

\begin{equation}
	\label{eq:bhh:optimisation_step:map:gamma1_update_operation}
	\begin{split}
		\gamma_{1,k}(t+1) = N_{1,k} + \gamma_{1,k}(t)
	\end{split}
\end{equation}

\begin{equation}
	\label{eq:bhh:optimisation_step:map:gamma2_update_operation}
	\begin{split}
		\gamma_{2,k}(t+1) = N_{0,k} + \gamma_{2,k}(t)
	\end{split}
\end{equation}

@@

@@

	\caption{Empirical results showing normalised average rank and statistics for the bottom six low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}

@@

Figure \ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each heuristic, per dataset. The heuristics are ordered according to the normalised ranks presented in Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b}. Figure \ref{fig:results:standalone:descriptive:descriptive} shows that the \textit{bhh\_gd} heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics. The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.

\begin{figure}[htb]
	\centering
	\includegraphics[width=\textwidth]{standalone_descriptive.pdf}
	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all independent runs and epochs.}
	\label{fig:results:standalone:descriptive:descriptive}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=\textwidth]{standalone_cd_overall.pdf}
	\caption{Critical difference plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
	\label{fig:results:standalone:descriptive:cd}
\end{figure}

@@

>>>>

\usepackage{acro}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{url}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{lineno}
\usepackage{xcolor}

@@

	\affiliation[aff:tuks]{
		organization={University of Pretoria},
		% addressline={Lynnwood Rd},
		city={Pretoria},
		% postcode={0002},
		state={Gauteng},
		country={South Africa}
	}

	\affiliation[aff:stellenbosch]{
		organization={Stellenbosch University},
		% addressline={Ryneveld Street},
		city={Stellenbosch},
		% postcode={7602},
		state={Western Cape},
		country={South Africa}
	}

	% Center for Applied Mathematics and Bioinformatics, Gulf University for Science and Technology, Kuwait
	\affiliation[aff:kuwait]{
		organization={Center for Applied Mathematics and Bioinformatics, Gulf University for Science and Technology},
		% addressline={Ryneveld Street},
		city={Mishref},
		country={Kuwait}
	}

	\affiliation[aff:wits]{
		organization={University of the Witwatersrand},
		% addressline={1 Jan Smuts Ave},
		city={Johannesburg},
		% postcode={2000},
		state={Gauteng},
		country={South Africa}
	}

	\author[aff:tuks]{\corref{cor1}A.N.~Schreuder}
	\ead{an.schreuder@up.ac.za}
	\author[aff:tuks]{A.S.~Bosman}
	\ead{annar@cs.up.ac.za}
	\author[aff:stellenbosch,aff:kuwait]{A.P.~Engelbrecht}
	\ead{engel@sun.ac.za}
	\author[aff:wits]{C.W.~Cleghorn}
	\ead{christopher.cleghorn@wits.ac.za}

@@

\linenumbers

@@

A popular field of focus for studying \acfp{ANN} is the process by which these models are trained. \acp{ANN} are trained by optimisation algorithms known as heuristics. Many different heuristics have been developed and used to train \acp{ANN} \citep{ref:rakitianskaia:2012}. Each heuristic has different search behaviours, characteristics, strengths and weaknesses. It is necessary to find the best heuristic to train \acp{ANN} in order to yield optimal results. This process is often non-trivial and time-consuming. Selection of the best heuristic to train \acp{ANN} is often problem specific \citep{ref:allen:1996}.

@@

This research takes a particular interest in developing a population-based, selection \acs{HH} that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process. This paper presents a novel \acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a heuristic selection probability distribution.

The general concept of the \acs{BHH} is summarised as follows: the \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics. These low-level heuristics are applied to a population of entities, each implementing a candidate solution to a \acs{FFNN}. The intent of the \acs{BHH} is to optimise both the underlying \acs{FFNN} and the \acs{FFNN} training process. The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process. These probabilities are then used as heuristic selection probabilities in the next step of the training process.

The update of selection probabilities is guided by Bayesian analysis, where prior probabilities are updated with new evidence to form posterior probabilities. The performance of each heuristic-entity combination is logged, which captures the efficacy of each heuristic applied to their respective entity, at different stages of the training process. The logged performance data acts as new evidence for the Bayesian analysis process. The \acs{BHH} also incorporates a novel proxied heuristic update step, where various components of the update step for low-level heuristics are sourced from other heuristics in the pool of heuristics, when the direct application of a heuristic is not feasible/possible.

@@

Although this research takes a particular interest in training \acp{FFNN}, the \acs{BHH} is not limited to these types of models and can generally be applied to any \acs{ANN} as long as the \acs{ANN} can be trained by all of the low-level heuristics. Experimentation with other \acp{ANN} architectures besides \acp{FFNN} is left for future research.

@@

% ARTIFICIAL NEURAL NETWORKS
\section{Artificial Neural Networks}
\label{sec:anns}

@@

The biggest difference between \acp{MH} and gradient-based heuristics is that \acp{MH} make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search space \citep{ref:blum:2003}. This also means that \acp{MH} do not necessarily require the error function to be differentiable. \citet{ref:blum:2003} provide advantages of \acp{MH} that include the following: they are easy to implement, they are problem independent and do not require problem-specific knowledge, and they are generally designed to find global optima, while gradient-based approaches can get stuck in local optima more often. Similar to gradient-based heuristics, a number of different meta-heuristics have been used to successfully train \acp{FFNN} \citep{ref:rakitianskaia:2012, ref:vanwyk:2014, ref:gupta:1999}. This research takes a particular interest in population-based \acp{MH} that have been used to train \acp{FFNN}. These include \acf{PSO} \citep{ref:abdulkarim:2021}, \acf{DE} \citep{ref:xue:2022}, and \acfp{GA} \citep{ref:khan:2012}.

@@

\citet{ref:burke:2010} propose a classification scheme used to classify \acp{HH}. According to the proposed classification scheme, \acp{HH} are classified in two dimensions. These include the \textit{source of feedback} used during learning and the nature of the \textit{heuristic search space}. For the dimension that involves the source of feedback, \acp{HH} can be classified as either \textit{no learning}, \textit{online learning} or \textit{offline learning}. For the dimension that involves the nature of the \textit{heuristic search space}, \acp{HH} can be classified as either \textit{heuristic selection} or \textit{heuristic generation}. Further distinction is made between \textit{construction} of heuristics and \textit{perturbation} of heuristics.

@@

@@

This section presents the novel \acs{BHH} and is structured as follows: Section \ref{sec:bhh:overview} presents an overview of the \acs{BHH}, Sections \ref{sec:bhh:heuristic_pool} - \ref{sec:bhh:selection_mechanism} provide details on the most important components of the \acs{BHH}, Section \ref{sec:bhh:optimisation_step} describes the optimisation step implemented by the \acs{BHH} and Section \ref{sec:bhh:hyper_parameters} discusses the hyper-parameters used by the \acs{BHH}.

\subsection{Overview}\label{sec:bhh:overview}

According to the classification scheme for \acp{HH} by \citet{ref:burke:2010}, the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.

The \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics. These low-level heuristics are applied to a population of entities, each implementing a candidate solution to a \acs{FFNN}. The intent of the \acs{BHH} is to optimise both the underlying \acs{FFNN} and the \acs{FFNN} training process. The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process. These probabilities are then used as heuristic selection probabilities in the next step of the training process.

The update of selection probabilities is guided by Bayesian analysis, where prior probabilities are updated with new evidence to form posterior probabilities. The performance of each heuristic-entity combination is logged, which captures the efficacy of each heuristic applied to their respective entity, at different stages of the training process. The logged performance data acts as new evidence for the Bayesian analysis process. The \acs{BHH} also incorporates a novel proxied heuristic update step, where various components of the update step for low-level heuristics are sourced from other heuristics in the pool of heuristics, when the direct application of a heuristic is not feasible/possible.

Figure \ref{fig:bhh_architecture} provides an illustration of the high-level architecture of the \acs{BHH}. Algorithm \ref{algo:bhh} provides the high level pseudo-code implementation of the \acs{BHH}. Discussions follow on the most important components of the \acs{BHH}.

@@

\begin{equation}
	\label{eq:bhh:optimisation_step:map:alpha_update_operation}
	\alpha_{k}(t+1) = N_{k} + \alpha_{k}(t)
\end{equation}

\begin{equation}
	\label{eq:bhh:optimisation_step:map:beta_update_operation}
	\beta_{j,k}(t+1) = N_{j,k} + \beta_{j,k}(t)
\end{equation}

\begin{equation}
	\label{eq:bhh:optimisation_step:map:gamma1_update_operation}
	\gamma_{1,k}(t+1) = N_{1,k} + \gamma_{1,k}(t)
\end{equation}

\begin{equation}
	\label{eq:bhh:optimisation_step:map:gamma2_update_operation}
	\gamma_{2,k}(t+1) = N_{0,k} + \gamma_{2,k}(t)
\end{equation}

\vspace{5mm}

@@

A population size of 5 is chosen as it empirically and consistently provides good results. The population size has a lower bound of 4, which is the highest, minimum number of entities required by any low-level heuristic used in this research. Furthermore, ablation studies \citep{ref:schreuder:2022} have shown that a smaller population size is generally better, since the Bayesian analysis process implemented by the \acs{BHH} has less, but more concentrated performance information from which it has to learn.

@@

	\caption{Empirical results showing normalised average rank and statistics for the bottom seven low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}

@@

Tables \ref{tab:results:standalone:metrics:accuracy_a} and \ref{tab:results:standalone:metrics:accuracy_b} provide the empirical results in accuracy format for the classification datasets. The accuracy is measured at the maximum epoch (30).
	\caption{Empirical results showing average accuracy at the max epoch (30) along with statistics for the top six low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
	\label{tab:results:standalone:metrics:accuracy_a}%
		\begin{tabular}{r|llllll}
			                                   & \multicolumn{6}{c}{\textbf{BHH vs. Low-Level Heuristics - Average accuracy at 30 epochs (Part A)}}                                                                                                                                                                                                                                                                                         \\
			\cmidrule{2-7}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adagrad}}                                                               & \multicolumn{1}{c}{\textbf{adam}}                     & \multicolumn{1}{c}{\textbf{rmsprop}}                  & \multicolumn{1}{c}{\textbf{bhh\_gd}}                  & \multicolumn{1}{c}{\textbf{nag}}                      & \multicolumn{1}{c}{\textbf{bhh\_all}}                 \\
			\textbf{abalone}                   & \cellcolor[rgb]{ .412,  .753,  .486}27.66\% (+-0.014)                                              & \cellcolor[rgb]{ .545,  .792,  .494}27.17\% (+-0.013) & \cellcolor[rgb]{ .388,  .745,  .482}27.74\% (+-0.016) & \cellcolor[rgb]{ .824,  .871,  .51}26.17\% (+-0.014)  & \cellcolor[rgb]{ .557,  .796,  .494}27.14\% (+-0.014) & \cellcolor[rgb]{ 1,  .922,  .518}25.52\% (+-0.021)    \\
			\textbf{bank}                      & \cellcolor[rgb]{ .608,  .808,  .498}90.15\% (+-0.003)                                              & \cellcolor[rgb]{ .388,  .745,  .482}90.33\% (+-0.003) & \cellcolor[rgb]{ .482,  .773,  .49}90.25\% (+-0.003)  & \cellcolor[rgb]{ .949,  .906,  .518}89.88\% (+-0.003) & \cellcolor[rgb]{ .882,  .89,  .514}89.94\% (+-0.003)  & \cellcolor[rgb]{ 1,  .922,  .518}89.84\% (+-0.003)    \\
			\textbf{car}                       & \cellcolor[rgb]{ .71,  .839,  .502}92.24\% (+-0.013)                                               & \cellcolor[rgb]{ .388,  .745,  .482}96.64\% (+-0.011) & \cellcolor[rgb]{ .427,  .757,  .486}96.13\% (+-0.018) & \cellcolor[rgb]{ .647,  .82,  .498}93.13\% (+-0.013)  & \cellcolor[rgb]{ .918,  .898,  .514}89.39\% (+-0.019) & \cellcolor[rgb]{ .612,  .812,  .498}93.59\% (+-0.017) \\
			\textbf{diabetic}                  & \cellcolor[rgb]{ .604,  .808,  .498}58.14\% (+-0.004)                                              & \cellcolor[rgb]{ .996,  .902,  .514}57.23\% (+-0.004) & \cellcolor[rgb]{ .769,  .855,  .506}57.85\% (+-0.004) & \cellcolor[rgb]{ .82,  .871,  .51}57.76\% (+-0.006)   & \cellcolor[rgb]{ .388,  .745,  .482}58.53\% (+-0.003) & \cellcolor[rgb]{ .988,  .757,  .482}55.42\% (+-0.024) \\
			\textbf{iris}                      & \cellcolor[rgb]{ .996,  .902,  .514}92\% (+-0.046)                                                 & \cellcolor[rgb]{ .627,  .816,  .498}94.89\% (+-0.042) & \cellcolor[rgb]{ .408,  .753,  .486}96.33\% (+-0.035) & \cellcolor[rgb]{ 1,  .922,  .518}92.44\% (+-0.077)    & \cellcolor[rgb]{ .388,  .745,  .482}96.44\% (+-0.037) & \cellcolor[rgb]{ .902,  .894,  .514}93.11\% (+-0.056) \\
			\textbf{mushroom}                  & \cellcolor[rgb]{ .522,  .784,  .49}99.97\% (+-0)                                                   & \cellcolor[rgb]{ .471,  .769,  .49}99.98\% (+-0.001)  & \cellcolor[rgb]{ .388,  .745,  .482}100\% (+-0)       & \cellcolor[rgb]{ .471,  .769,  .49}99.98\% (+-0)      & \cellcolor[rgb]{ 1,  .922,  .518}99.84\% (+-0.001)    & \cellcolor[rgb]{ .537,  .788,  .494}99.96\% (+-0.001) \\
			\textbf{wine\_quality}             & \cellcolor[rgb]{ .541,  .788,  .494}55.06\% (+-0.014)                                              & \cellcolor[rgb]{ .388,  .745,  .482}55.62\% (+-0.013) & \cellcolor[rgb]{ .592,  .804,  .494}54.86\% (+-0.011) & \cellcolor[rgb]{ 1,  .922,  .518}53.35\% (+-0.017)    & \cellcolor[rgb]{ .651,  .824,  .498}54.64\% (+-0.015) & \cellcolor[rgb]{ .941,  .906,  .518}53.57\% (+-0.015) \\
		\end{tabular}%
	\caption{Empirical results showing average accuracy at the max epoch (30) along with statistics for the bottom seven low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
	\label{tab:results:standalone:metrics:accuracy_b}%
		\begin{tabular}{r|lllllll}
			                                   & \multicolumn{7}{c}{\textbf{BHH vs. Low-Level Heuristics - Average accuracy at 30 epochs (Part B)}}                                                                                                                                                                                                                                                                                                                                                \\
			\cmidrule{2-8}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adadelta}}                                                              & \multicolumn{1}{c}{\textbf{bhh\_mh}}                  & \multicolumn{1}{c}{\textbf{ga}}                       & \multicolumn{1}{c}{\textbf{pso}}                      & \multicolumn{1}{c}{\textbf{sgd}}                      & \multicolumn{1}{c}{\textbf{momentum}}                 & \multicolumn{1}{c}{\textbf{de}}                      \\
			\textbf{abalone}                   & \cellcolor[rgb]{ .659,  .824,  .498}26.76\% (+-0.013)                                              & \cellcolor[rgb]{ .992,  .839,  .498}23.32\% (+-0.018) & \cellcolor[rgb]{ .988,  .733,  .478}20.52\% (+-0.019) & \cellcolor[rgb]{ .984,  .651,  .463}18.31\% (+-0.029) & \cellcolor[rgb]{ .996,  .878,  .506}24.42\% (+-0.017) & \cellcolor[rgb]{ .996,  .875,  .506}24.29\% (+-0.015) & \cellcolor[rgb]{ .973,  .412,  .42}11.81\% (+-0.044) \\
			\textbf{bank}                      & \cellcolor[rgb]{ .988,  .918,  .518}89.85\% (+-0.003)                                              & \cellcolor[rgb]{ .992,  .784,  .49}89.44\% (+-0.004)  & \cellcolor[rgb]{ .98,  .573,  .447}88.79\% (+-0.004)  & \cellcolor[rgb]{ .976,  .494,  .435}88.56\% (+-0.006) & \cellcolor[rgb]{ .98,  .596,  .455}88.86\% (+-0.004)  & \cellcolor[rgb]{ .984,  .643,  .463}89.01\% (+-0.003) & \cellcolor[rgb]{ .973,  .412,  .42}88.3\% (+-0.004)  \\
			\textbf{car}                       & \cellcolor[rgb]{ 1,  .922,  .518}88.25\% (+-0.018)                                                 & \cellcolor[rgb]{ .988,  .714,  .475}80.74\% (+-0.034) & \cellcolor[rgb]{ .973,  .459,  .427}71.52\% (+-0.022) & \cellcolor[rgb]{ .988,  .725,  .478}81.16\% (+-0.035) & \cellcolor[rgb]{ .973,  .412,  .42}69.78\% (+-0.027)  & \cellcolor[rgb]{ .973,  .439,  .424}70.86\% (+-0.019) & \cellcolor[rgb]{ .973,  .416,  .42}69.98\% (+-0.034) \\
			\textbf{diabetic}                  & \cellcolor[rgb]{ .482,  .773,  .49}58.36\% (+-0.003)                                               & \cellcolor[rgb]{ .992,  .847,  .502}56.53\% (+-0.006) & \cellcolor[rgb]{ .98,  .624,  .459}53.82\% (+-0.003)  & \cellcolor[rgb]{ .984,  .655,  .467}54.22\% (+-0.011) & \cellcolor[rgb]{ .992,  .922,  .518}57.45\% (+-0.004) & \cellcolor[rgb]{ 1,  .922,  .518}57.43\% (+-0.002)    & \cellcolor[rgb]{ .973,  .412,  .42}51.21\% (+-0.059) \\
			\textbf{iris}                      & \cellcolor[rgb]{ .976,  .525,  .439}83.22\% (+-0.063)                                              & \cellcolor[rgb]{ .984,  .918,  .518}92.56\% (+-0.062) & \cellcolor[rgb]{ .988,  .757,  .486}88.67\% (+-0.091) & \cellcolor[rgb]{ .816,  .871,  .51}93.67\% (+-0.042)  & \cellcolor[rgb]{ .973,  .412,  .42}80.56\% (+-0.098)  & \cellcolor[rgb]{ .973,  .424,  .42}80.89\% (+-0.084)  & \cellcolor[rgb]{ .98,  .596,  .455}84.89\% (+-0.099) \\
			\textbf{mushroom}                  & \cellcolor[rgb]{ .569,  .796,  .494}99.95\% (+-0.001)                                              & \cellcolor[rgb]{ .996,  .898,  .51}97.77\% (+-0.007)  & \cellcolor[rgb]{ .984,  .671,  .467}76.78\% (+-0.112) & \cellcolor[rgb]{ .996,  .906,  .514}98.67\% (+-0.009) & \cellcolor[rgb]{ .992,  .824,  .498}91.08\% (+-0.008) & \cellcolor[rgb]{ .992,  .804,  .494}89.11\% (+-0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}52.58\% (+-0.028) \\
			\textbf{wine\_quality}             & \cellcolor[rgb]{ .647,  .82,  .498}54.66\% (+-0.012)                                               & \cellcolor[rgb]{ .992,  .835,  .498}51.52\% (+-0.014) & \cellcolor[rgb]{ .988,  .733,  .478}49.26\% (+-0.017) & \cellcolor[rgb]{ .984,  .686,  .471}48.21\% (+-0.038) & \cellcolor[rgb]{ .996,  .867,  .506}52.14\% (+-0.014) & \cellcolor[rgb]{ .992,  .831,  .498}51.38\% (+-0.014) & \cellcolor[rgb]{ .973,  .412,  .42}42.1\% (+-0.042)  \\
		\end{tabular}%

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{standalone_cd_overall.pdf}
	\caption{Critical difference plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
	\label{fig:results:standalone:descriptive:cd}
\end{figure}

@@

Section \ref{sec:bhh:hyper_parameters} presented the \acs{BHH} hyper-parameters. A number of ablation studies were done in the interest of finding good hyper-parameters for the baseline \acs{BHH} \citep{ref:schreuder:2022}. A summary of these ablation studies on different hyper-parameter configurations is given in Table \ref{tab:methodology:experiments:bhh_variants} along with a brief conclusion of the outcomes.

\begin{table}[htbp]
	\centering
	\caption{BHH variants and their configuration. The \index{heuristic pool}heuristic pool configuration \textit{gd} refers to the \index{heuristic pool}heuristic pool configuration where only gradient-based \index{heuristic}heuristics are included, and \textit{mh} refers to the \index{heuristic pool}heuristic pool configuration where only \acp{MH} are included.}
	\label{tab:methodology:experiments:bhh_variants}%
	\par\bigskip
	\resizebox{0.9\textwidth}{!}{
		\begin{tabular}{ccc}
			\textbf{hyper-parameter} & \textbf{considered}                   & \textbf{conclusion}       \\
			\midrule
			heuristic pool           & all, gd, mh                           & gd performed best         \\
			population               & 5, 10, 15, 20, 25                     & smaller is better         \\
			credit                   & ibest, pbest, rbest, gbest, symmetric & problem dependent         \\
			reselection              & 1, 5, 10, 15, 20                      & larger is better          \\
			replay                   & 1, 5, 10, 15, 20                      & problem dependent         \\
			reanalysis               & 1, 5, 10, 15, 20                      & problem dependent         \\
			burn in                  & 0, 5, 10, 15, 20                      & lower is better           \\
			normalise                & false, true                           & no significant difference \\
			discounted rewards       & false, true                           & no significant difference \\
		\end{tabular}%
	}
\end{table}%

A general finding in the ablations studies revealed the inter-dependencies between the hyper-parameters. For example, there is an inter-dependency between the \textit{reselection}, \textit{replay}, and \textit{reanalysis} hyper-parameters. This can be seen in the ablation studies that focussed on the \textit{normalise} and \textit{discounted rewards} hyper-parameters. The default \textit{replay window size} (10) hyper-parameter, results in a scenario where the logged performance data is too little for the \textit{normalise} and \textit{discounted rewards} hyper-parameters to make a statistically significant impact.

Furthermore, the ablation studies on the \textit{replay} and \textit{reanalysis} hyper-parameters, which resulted in problem dependent outcomes, illustrates that a dynamic, online-learning approach is required, since some problems benefit from maintaining many records in the performance log, while others do not.
